GeoSPARQL 1.1: an almost decadal update to the most important geospatial LOD standard

### 2021-04-21 manuscript.tex
minor updates, ReviewCahnges file added

In parallel, the OGC API Features standard \cite{ogcapifeaturespart3} is developed, which also proposes functions for filtering feature collections. While OGC API Features proposes the use of the Common Query Language (CQL) for filtering, it is also open to other query language implementations such as GeoSPARQL. When comparing the filter capabilities of CQL to GeoSPARQL, one can observe that concerning spatial filter capabilities, the two query languages provide comparable functionality. However, the version of CQL proposed by OGC API Features also provides support of spatiotemporal operators, which may be an addition to be further explored in the contiuous GeoSPARQL development process.

>>>>

Coincident with GeoSPARQL 1.1 development, the OGC API Features standard \cite{ogcapifeaturespart3} is being developed. It also proposes functions for filtering feature collections. While OGC API Features proposes the use of the Common Query Language (CQL) for filtering, it is also open to other query language implementations such as GeoSPARQL. When comparing the filter capabilities of CQL to GeoSPARQL, one can observe that the two query languages provide comparable spatial functionality, however the CQL proposed also supports spatiotemporal operators, which may be an addition to GeoSPARQL to be further explored in its contiuous development process.
